\Large \bf Module Dialysis with Lya

### 2019-12-20 paper/draft.tex
Update abstract

% TODO: tempted to term this "Module-aware dynamic fracture, analysis, and reassembly" as Dialysis or refracture
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix2019_v3}

@@

@@

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Module-level Dynamic Analysis}

%for single author (just remove % characters)
\author{
{\rm Anonymous Author(s)}\\
Submission \#323, 12 pages; Additional Material:
% {\rm Grigoris Ntousakis}\\
% Technical University of Crete
% \and
% {\rm Nikos Vasilakis}\\
% Massachusetts Institute of Technology
}

@@

\begin{abstract}
Modern software relies extensive on third-party libraries:
  recent studies on several ecosystems show that code written by an application's nominal developers is only a small fraction of its total line count.
Such over-reliance creates many challenges that appear later in the development process, exactly because developers have little knowledge and understanding of the module's internals.
For example, security auditing and performance profiling large applications in the presence of deeply-nested third-party code becomes cumbersome.

We introduce \emph{module dialysis}, a technique for dynamic analysis specifically tailored to module boundaries.
Module dialysis can be bolted on existing language runtime environments in a language-agnostic fashion, and enables module-aware application fracture, analysis, and reassembly at runtime.
Dialysis supports dynamic application fragmentation, analysis, and re-assembly at the level of individual modules.
Tailored at providing information at the (recursive) boundaries of third-party modules.
Such modules can be part of third-party packages or of the language's standard library;
  the latter is important for resources that are part of the broader environment where the application is executing, such as the operating system and the network.
By leveraging the ubiquity of third-party modules in today's applications, this analysis provides insights k

>>>>

% TODO: tempted to term this "Module-aware dynamic fragmentation, analysis, and reassembly" as Dialysis or refracture
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix2019_v3}

@@

\newcommand{\fra}{fragmentation\xspace} % fracture
\newcommand{\ana}{analysis\xspace}      % 
\newcommand{\ass}{reassembly\xspace}    % 
\newcommand{\dia}{\fra, \ana, and \ass}

@@

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Module Dialysis with Lya}

%for single author (just remove % characters)
\author{
{\rm Anonymous Author(s)}\\
Submission \#225, 12 pages; Additional Material:
% {\rm Grigoris Ntousakis}\\
% Technical University of Crete
% \and
% {\rm Nikos Vasilakis}\\
% Massachusetts Institute of Technology
}

@@

\begin{abstract}

This paper introduces \emph{module dialysis}, a novel technique for dynamic analysis specifically tailored to module boundaries. % to applications with many modules
Modules are becoming the cornerstone of modern software engineering:
  applications today use hundreds of modules, to the point where code written by their nominal developers is becoming only a small fraction of their total line count.
On the surface, such code reuse is beneficial, as it lowers development costs, software testing, encapsulation; 
  however, such over-reliance creates many challenges later in the development process, exactly because developers have little knowledge and understanding of module's internals.
For example, security auditing and performance profiling---which are already challenging for monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.

% Turn such over-reliance on its head
To address these challenges, module dialysis enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual modules.
One of its highlights is ease of deployment and use:
  (i) bolted onto existing runtime environments as a library, by wrapping and transforming the underlying module system
  (ii) allowing developers to extract information using the same abstractions as the host language---eschewing low-level instrumentation.
Due to the in the host language and at a coarser granularity than full-fledged dynamic analysis, module dialysis has the potential of low performance overheads while still providing important information.

Our dialysis prototype, \sys, targets the JavaScript ecosystem through the V8 runtime.
We use a series of case-studies to motivate \sys's design, and demonstrate how \sys allows the analysis of both individual modules as well as multi-module application programs---all with a surprisingly low developer effort.
Experiments with \sys show that it adds a virtually imperceptible increase in the load latency of individual modules and that it scales well to real applications with hundreds of modules.

module-level analysis

 and demonstrate how \sys provides high-performance by shadowing variables and transforming and wrapping values

Module dialysis can be bolted on existing language runtime environments in a language-agnostic fashion 
% By leveraging the ubiquity of third-party modules in today's applications
Such modules can be part of third-party packages or of the language's standard library;
  the latter is important for resources that are part of the broader environment where the application is executing, such as the operating system and the network.
By leveraging the ubiquity of third-party modules in today's applications, this analysis provides insights k
